\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
Updates to theorems with HILL entropy

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume there exists a PPT-distinguisher $D$ such that $\delta^D((\vA, \vA X+E), (\vA, U))>\epsilon$ for non-negligible $\epsilon$ and $\vA\in \Fq^{m\times n}, X\in \Fq^{n}, U\in \Fq^m$ drawn uniformly and $E$ drawn uniformly from $[-\rho q, \rho q]$.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ in the worst case.
\end{lemma}

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:conversion to unpredictability}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

@@

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m- \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$.  Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

@@

\section{\lemref{lem:conversion to unpredictability}}
\label{sec:proof of unpred conversion}
In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.  %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).  Thus, we have the following claim:
%\begin{claim}
%\label{lem:unp of x and e}
%Let $A, X, E$ be as above, then:
%\begin{itemize}
%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
%\end{itemize}
%\end{claim}
%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
%\begin{assumption}
%\label{assume:entropy LWE}
%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.  
%\end{assumption}
%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
\end{lemma}

\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.  Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.  Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.  By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.  To expand to $E$ we use the following claim:

\begin{claim}
Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
\[
H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
\]
\end{claim}
%\begin{claim}
%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
%\end{claim}
%\begin{proof}
%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%\end{proof}

%\begin{claim}
%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
%\end{claim}
%\begin{proof}
%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.  Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.  Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.  Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.  Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
%This completes the claim.
%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.  In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%\end{proof}

%\begin{claim}
%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
%\end{claim}
%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.  This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.  Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
%
%
%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.  By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.  This completes the proof of \lemref{lem:conversion to unpredictability}.
%\end{proof}
\begin{proof}
Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.  We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.  That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.  Fix one such $Y$.  Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.  Note that $\mathcal{E}$ occurs with probability $1-\gamma$.

Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
\begin{align*}
\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
\end{align*}
Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.  Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$. Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.

We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
\begin{enumerate}
\item Input $(\vA, \vA X+E)$.
\item Run $y\leftarrow C(\vA, \vA X+E)$.
\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
\end{enumerate}
Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.  Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.  Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
\end{proof}

>>>>

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$. Assume decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard to approximate with the factor $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi = [-\rho q, \rho q]$, the $\distLWE_{n, m, q, \chi}$ is $(\epsilon, \poly(n))\mbox{-}$hard, where $\epsilon = \ngl(n)$.
\end{lemma}

We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show there are many bits of $X$ that are unpredictable.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
\end{lemma}

%\begin{lemma}
%\label{lem:conversion to unpredictability}
%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
%\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} we can use the code-offset construction in \consref{cons:informal construction} and retain HILL entropy $k\log q$.  
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch time $s_{sketch} = O(n^3\log n)$, and recover time $s_{rec}= O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

@@

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$.  Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

@@

%\section{\lemref{lem:conversion to unpredictability}}
%\label{sec:proof of unpred conversion}
%In this section we show that for an indistinguishable LWE instance, the unpredictability entropy of $E$ conditioned on $\vA X+E$ remains high.  %We first note that any inverter that can recover $X$ can recover $E$ and vice versa by using simple a single addition and multiplication~(and vice versa).  Thus, we have the following claim:
%%\begin{claim}
%%\label{lem:unp of x and e}
%%Let $A, X, E$ be as above, then:
%%\begin{itemize}
%%\item $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E)\geq k \Rightarrow H^{\unp}_{\epsilon, s'}(E| \vA, \vA X+E) \geq k$ for $s'\approx s$.
%%\item $H^{\unp}_{\epsilon, s}(E | \vA, \vA X+E) \geq k \Rightarrow H^{\unp}_{\epsilon', s'}(X | \vA, \vA X+E) \geq k'$ for $k'\approx k, \epsilon' \approx \epsilon, s'\approx s$. 
%%\end{itemize}
%%\end{claim}
%%In the body of the text we use \lemref{lem:unp of x and e} to present  \assref{assume:indist LWE} in terms of unpredictability entropy~(\assref{assume:entropy LWE}).
%%We now restate Assumption~\ref{assume:indist LWE} in terms of unpredictability entropy:
%%\begin{assumption}
%%\label{assume:entropy LWE}
%%Let $n$ be a security parameter, let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be prime and let $\chi$ be a distribution on $\Fq$.  If $X\in\Fq^n, A\in\Fq^{m\times n}$ are chosen uniformly at random and $E$ is chosen according to $\chi$, $H^{\unp}_{\epsilon, s}(X | A, AX+E) =H^{\unp}_{\epsilon, s'}(E| A, AX+E) \geq m\log q $ for $s'\approx s$.  
%%\end{assumption}
%%For clarity, we delay the proof of \clref{lem:unp of x and e} until the end of this section~(the proof is quite straightforward).
%We first recall a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009}.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
%\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
%\label{lem:many hardcore bits}
%Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )= k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
%\end{lemma}
%
%\begin{proof}[Proof of \lemref{lem:conversion to unpredictability}]
%Assume that $\distLWE_{(n-k, m, q, \chi)}$ is $(\epsilon, s_{sec})$ hard and that $m\geq n$.  Let $\vA\in \zq^{m\times n}, X\in \zq^n$ and $E$ be distributed according to $\chi^m$.  Then according to \lemref{lem:many hardcore bits} we know that $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA , \vA X+E)\geq k\log q$.  By \lemref{lem:hillimplyunpimplyyao}, we know that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA, \vA X+E)\geq k\log q$.  To expand to $E$ we use the following claim:
%
%\begin{claim}
%Let $\vA, X, E$ be distributed as in \lemref{lem:conversion to unpredictability} and $m\geq n$ and let $k\leq n$.  Then 
%\[
%H^{\unp}_{\epsilon', s_{sec}'} ( E | \vA X+ E) \geq H^{\unp}_{\epsilon, s_{sec}} ( X_{1,..., k} | \vA X+E)
%\]
%\end{claim}
%%\begin{claim}
%%If $H^{\unp}_{0, s}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{0, s}(X|Z)\geq k$.
%%\end{claim}
%%\begin{proof}
%%Suppose that $H^{\unp}_{0, s}(X|Z)< k$ that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%%\end{proof}
%
%%\begin{claim}
%%If $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | Z) \geq k$ then $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)\geq k$ for $s_{sec} \approx s_{sec}'$.
%%\end{claim}
%%\begin{proof}
%%Assume that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,...,k}|Z)\geq k$.
%%Suppose that $H^{\unp}_{\epsilon, s_{sec}'}(X|Z)< k$.  Let $Y$ be a distribution such that $\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Furthermore, let $C$ be a circuit of size at most $s_{sec}'$ where $\Pr[C(Z) = Y] > 2^{-k}$.  Define the circuit $C'$ that outputs the first $k$ bits of $C$'s output.  Thus, $\Pr[C'(Z) = Y_{1,..., k}] \geq \Pr[C(Z) = Y] > 2^{-k}$.  Note that $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,...,k}, Z), (Y_{1,..., k}, Z))<\delta^{\mathcal{D}_{s_{sec}'}}((X, Z), (Y, Z))\leq \epsilon$.  Together, these two facts contradict $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k}|Z)\geq k$.
%%This completes the claim.
%%\bnote{This claim isn't accurate because we can't show for all $Y_{1,..., k}$.  In order to complete the proof we need to show that $\forall Y_{1,..., k}$ such that $(X_{1,..., k}, Z), (Y_{1,...k}, Z)<\epsilon$ there exists an extension which is also indistinguishable.}
%% that is there exists a circuit $C$ of size at most $s$ such that $\Pr[C(Z) = X]> 2^{-k}$.  Then let $C'$ be a circuit that simply takes the output of $C$ and returns the first $k$ bits.  Then $\Pr[C'(Z) = X_{1,...,k}]\geq \Pr[C(Z) = X] > 2^{-k}$.  This completes the claim.
%%\end{proof}
%
%%\begin{claim}
%%If $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} | Z)\geq k$ then $H^{\yao}_{\epsilon , s_{sec}'}(X|Z)\geq k$ for $s_{sec}\approx s_{sec}'$.
%%\end{claim}
%%Suppose that $H^{\yao}_{\epsilon, s_{sec}}(X_{1,..., k} |Z ) \geq k$.  This implies $\exists c, d$ of total size $s_{sec}$ where $c$ has outputs of length $\ell$ such that $\Pr[d(c(X_{1,..., k}, Z), Z) = X_{1,..., k}] \leq 2^{\ell -k} + \epsilon$.  Furthermore, suppose $\forall c', d'$ of total size $s_{sec}$ where $c$ has output length $\ell$ and $\Pr[d(c(X), Z), Z) = X] > 2^{\ell-k} +\epsilon$.
%%
%%
%%Thus, we know that $H^{\unp}_{\epsilon, s_{sec}'}(X | \vA, \vA X+E)\geq k\log q$.  By \lemref{lem:unp of x and e} we know that $H^{\unp}_{\epsilon, s_{sec}'} (E | \vA, \vA X+E)\geq k\log q$.  This completes the proof of \lemref{lem:conversion to unpredictability}.
%%\end{proof}
%\begin{proof}
%Suppose that $H^{\unp}_{\epsilon', s_{sec}}( E | \vA X+E) < \ell$.  We will show that $H^{\unp}_{\epsilon, s_{sec}}(X_{1,..., k} | \vA X+E) < \ell$.  That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}'}}((E, \vA X+E), (Y, \vA+E))\leq \epsilon$, there exists $C$ of size $s_{sec}'$ such that $\Pr[C(\vA, \vA X+E) = Y]> 2^{-\ell}$.  Fix one such $Y$.  Let $\mathcal{E}$ be the event that $A_{1,..., n}^{-1}$ exists.  Note that $\mathcal{E}$ occurs with probability $1-\gamma$.
%
%Define the distribution $Y' =A^{-1}_{1,...,n}(\vA X+E -Y)$.  Then one has that 
%\begin{align*}
%\delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E))&\leq \delta^{\mathcal{D}_{s_{sec}}}((Y', \vA, \vA X+E ), (X, \vA, \vA X+E) |\mathcal{E} )+ \gamma\\
%&\leq \delta^{\mathcal{D}_{s_{sec}}}(\vA^{-1}_{1,..., n}(\vA X+E - Y), \vA, \vA X+E), (X, \vA, \vA X+E))+\gamma\\
%&\leq \delta^{\mathcal{D}_{s_{sec}'}}((Y, \vA, \vA X+E), (E, \vA, \vA X+E))+\gamma\leq \epsilon' + \gamma
%\end{align*}
%Where the second to last inequality follows by applying the transform $\vA X+E - \vA(\cdot)$ to the first argument.  Note  that $\delta^{\mathcal{D}_{s_{sec}}}((Y'_{1,...k}, \vA, \vA X+E ), (X_{1,..,k}, \vA, \vA X+E))\leq \epsilon' + \gamma$. Otherwise there would be a distinguisher for the entire distribution by just ignoring the last $n-k$ dimensions.
%
%We now show that $\exists C'$ such that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k}$.  Define $C'$ as follows:
%\begin{enumerate}
%\item Input $(\vA, \vA X+E)$.
%\item Run $y\leftarrow C(\vA, \vA X+E)$.
%\item Try to compute $\vA^{-1}_{1,.., n}$, if $\vA^{-1}_{1,..., n}$ does not exist output $\perp$.
%\item Output $z = \vA^{-1}_{1,..., n}(\vA X+E -y)$
%\end{enumerate}
%Observer that $\Pr[C'(\vA, \vA X+E) = Y']> 2^{-k} - \gamma$.  Finally note that $\exists C''$ that simply outputs the first $k$ dimensions of the output of $C'$.  Thus, $H^{\unp}_{\epsilon, s_{sec}}( X_{1,..., n}| \vA , \vA X+E)< 2^{-k} - \gamma$.
%\end{proof}
%
%The statement of \lemref{lem:conversion to unpredictability} follows by the statement of the claim.
%%\begin{proof}[Proof of \clref{lem:unp of x and e}]
%%First suppose that $H^{\unp}_{\epsilon, s}(X| \vA, \vA X+E) < k$.  That is, $\exists I \in\mathcal{D}_s$ such that for exists $Y$ where $\delta^{\mathcal{D}_s}((X, \vA, \vA X+E), (Y, \ A, \vA X+E)\leq \epsilon$, $\Pr[I(\vA, \vA X+E) = Y] > 2^{-k}$.  Define $I'$ by the following:
%%\begin{enumerate}
%%\item Input $(\vA, \vA X+E)$.
%%\item Run $y\leftarrow I(\vA, \vA X+E)$.
%%\item Output $z = \vA y - \vA X+E$.
%%\end{enumerate}
%%Note that $|I'|\approx |I|$.
%%It suffices to show that $\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, A, \vA X+E))\leq \epsilon$.  One has the following:
%%\begin{align*}
%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (Z, \vA, \vA X+E))&=
%%\delta^{\mathcal{D}_s'} ((E, \vA, \vA X+E), (\vA Y-\vA X+E, \vA, \vA X+E))\\
